Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2016-10-04 Experiments.tex
minor comments and fixes.

@@

On one hand, this execution strategy leads to a drastic reduction of the queue time and, consequently, it guarantees high-performances. On the other hand, this strategy is tailored for the execution of ATLAS workload on TITAN by using the Backfill queue\mtnote{Do we have a queue dedicated to backfilling on Titan or should we speak of backfilling done on one or more queues?}.

@@

As first, we investigate resource allocation as a function of time (wall-time) and space (number of nodes\mtnote{cores?}) in order to understand how TITAN's scheduler and workload behave under different allocation requests. This analysis includes two bulks of experiments: the first, generated ``in silico'', is based on simulations of the TITAN's scheduler by means of the Moab simulator, whereas the second, generated ``in vivo'',  considers real submissions of ATLAS workload on TITAN's batch queue.

>>>>

\jhanote{Not sure this should be under ``PANDA:Future/ROAD MAP?''}

@@

On one hand, this \jhanote{I would use the word execution strategy carefully. Maybe a more general term such as execution model, a special type of which is execution strategy?} execution strategy leads to a drastic reduction of the queue time and, consequently, it guarantees high-performances. On the other hand, this strategy is tailored for the execution of ATLAS workload on TITAN by using the Backfill queue\mtnote{Do we have a queue dedicated to backfilling on Titan or should we speak of backfilling done on one or more queues?}.

@@

First, we investigate resource allocation as a function of time (wall-time) and space (number of nodes\mtnote{cores?}) in order to understand how TITAN's scheduler and workload behave under different allocation requests. This analysis includes two bulks of experiments: the first, generated ``in silico'', is based on simulations of the TITAN's scheduler by means of the Moab simulator, whereas the second, generated ``in vivo'',  considers real submissions of ATLAS workload on TITAN's batch queue.
